\section{Abstract}
\label{ch:abstract}

If you like to spend your free time playing video games there is a high likelihood that you
experienced one of the biggest problems in the gaming industry: cheating. Cheating ruins the
competitive integrity of video games, and when it is widespread it can even damage the game by
making the players leave the game, causing a dwindling player base. Game developers have
tried numerous ways of fighting cheats, with varying success rates. A more innovative and less
explored way of anti-cheat development involves artificial intelligence. This paper aims to further explore the possibility
and effectiveness of using AI for cheat detection.

The problem we try to solve is that the gaming industry can not keep up with modern cheats, therefore there are several ways to cheat in recently popular games, no matter how strong the applied anti-cheat method is.

The problem covers a wide variety of different platforms and different types of video-games available on the market.
In order to get the best results possible we try solving the problem with a combination of different AI powered techniques, namely DNNs, explainable AI and more.

By implementing, testing, and deploying our AI-driven anti-cheat solution we aim to
demonstrate that AI can be more effective in identifying cheaters than traditional anti-cheating
measures. Our finished system gives game developers a chance to significantly reduce cheating
in their games, and maintain the integrity of competitive gaming.
