\section{Future Work}
\label{ch:future}

Despite the incredible results our research achieved we believe this system for cheat detection can still be improved in the future, further reducing cheats in video games. Our research may have concluded but we think the following ideas can give ambitious researchers inspiration to work on this topic further and improve cheat-free gaming even more in the future.

Even though we tried using the most advanced technologies currently available, there are still a lot of ways to improve upon the anti-cheat detection system we implemented. We tried to train the AI models with as much data as possible, but implementing this detection system in a popular video game and using the available user data from a larger player base could possibly further improve the models’ accuracy, reaching around 97.5\%. 

The usage of even more or diverse AI models could enhance the effectiveness of this system. Combining more AI models can improve certain, currently not covered ways of cheat detection. While this approach may not improve the cheat detection rate itself, it could broaden the range of cheats the system can detect.

Researching more on the types of data a cheat detection system like this can use for more accurate cheat recognition would also be a way to improve a similar system. The type of data we used proved effective but perhaps there is user or game data that gives away cheaters more simply or more obviously. Training the models with different, new types of data could possibly reduce the rate of cheating further, nearing 100\% cheat detection rate. 

Training the system to recognize returning cheat users and blocking them from playing or interacting with the game could also prove useful in preventing more cheating. Investigating the players who get removed from a game for cheating and returning with a different account could improve cheat prediction.